\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
log scale figure in manuscript

{\color{blue} For each replication we compute the ratio of the value of the loss function corresponding to each alternative reconciliation method relative to the loss function corresponding to base forecsats. A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window. We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available {\color{red} in an online supplement.}

For TSE, relative loss is always less than 1 only for OLS reconciliation, for Structural-WSE the same is only true for Structural-WLS and for Spend-WSE the same is only true for Spend-WLS.  Therefore, Figure~\ref{fig:BaseVSRecon_Fc} demonstrates that a reconciliation method is guaranteed to improve upon base forecasts only when the $\bm{W}$ used in the loss function and reconciliation coincide.  This is precisely what Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} would predict.  On the other hand, for every loss function, MinT will perform worse than base for some realisations.  For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$ and since the estimate of $\Sigma$ will change with each realisation we do not believe this is a sensible loss function to use.

@@

The advantage of MinT however is clearly seen when loss functions are averaged.  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation} 
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}.
}

>>>>

{\color{blue} For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts. A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window. We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available {\color{red} in an online supplement.}

For TSE, relative loss is always less than 1 only for OLS reconciliation, for Structural-WSE the same is only true for Structural-WLS and for Spend-WSE the same is only true for Spend-WLS.  Therefore, Figure~\ref{fig:BaseVSRecon_Fc} demonstrates that a reconciliation method is guaranteed to improve upon base forecasts only when the $\bm{W}$ used in the loss function and reconciliation coincide.  This is precisely what Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} would predict.  On the other hand, for every loss function, MinT will perform worse than base for some realisations.  For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$. Since the estimate of ${\bm\Sigma}$ will change with each replication we do not believe this is a sensible loss function to use.

@@

The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation} 
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}.
}
